\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-09-25 papers/jss/article.Rnw
Address some reviewer feedback about why we use RObjectTables and some of the pitfalls, with some of this text provided verbatim from Karl Millar, who is already thanked in the acknowledgements section.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@897 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

To create or parse a Protocol Buffer Message, one must first read in 
the message type specification from a \code{.proto} file. The 
\code{.proto} files are imported using the \code{readProtoFiles}
function, which can either import a single file, all files in a directory,
or every \code{.proto} file provided by a particular \proglang{R} package.

After importing proto files, the corresponding message descriptors are
available by name from the \code{RProtoBuf:DescriptorPool} environment in 
the \proglang{R} search path.  This environment is implemented with the 
user-defined tables framework from the \pkg{RObjectTables} package
available from the OmegaHat project \citep{RObjectTables}.  Instead of
being associated with a static hash table, this environment
dynamically queries the in-memory database of loaded descriptors
during normal variable lookup.

>>>>

To create or parse a Protocol Buffer Message, one must first read in 
the message type specification from a \code{.proto} file. 
A small number of message types are imported when the package is first
loaded, including the \code{tutorial.Person} type we saw in the last
section.
All other types must be imported from
\code{.proto} files using the \code{readProtoFiles}
function, which can either import a single file, all files in a directory,
or every \code{.proto} file provided by a particular \proglang{R} package.

After importing proto files, the corresponding message descriptors are
available by name from the \code{RProtoBuf:DescriptorPool} environment in 
the \proglang{R} search path.  This environment is implemented with the 
user-defined tables framework from the \pkg{RObjectTables} package
available from the OmegaHat project \citep{RObjectTables}.  Instead of
being associated with a static hash table, this environment
dynamically queries the in-memory database of loaded descriptors
during normal variable lookup.  This allows new descriptors to be
parsed from \code{.proto} files and added to the global
namespace.\footnote{Note that there is a significant performance
  overhead with this RObjectTable implementation.  Because the table
  is on the search path and isn't cacheable, lookups of symbols that
  are behind it in the search path can't be added to the global object
  cache, and R must perform an expensive lookup through all of the
  attached environments and the protocol buffer definitions to find common
  symbols (most notably those in base) from the global environment.
  Fortunately, proper use of namespaces and package imports reduces
  the impact of this for code in packages.}
